Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
removed paragraph in appendix + added todo
more todos

@@

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}). 
\item[2.] The second approach relies on computing a 
completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the 
generalisation step is given as an incremental
increase of precision and sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
\end{itemize}

>>>>

\todo{Dario, can you please shorten this?}

@@

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states,
  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}). 
\todo{Dario, can you briefly explain solution generalisation for your approach?}
\item[2.] The second approach uses a multi-staged validation phase
  and performes solution generalisation based on
the plant's precision, the number of loop unrollongs
and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
%%   relies on computing a 
%% completeness threshold $k$ for each loop such that it is sufficient to 
%% unroll the corresponding loop $k$ times. For this approach the 
%% generalisation step is given as an incremental
%% increase of precision and sampling rate 
\end{itemize}

\todo{Can we come up with some sort of figure that makes it easier to visualise
the generalisation step in each approach?}
